Synthesis of Linear Functional Programs

### 2021-05-09 article/article.tex
merge

Specifications can take many forms (e.g.  polymorphic refinement
types~\cite{DBLP:conf/pldi/PolikarpovaKS16},
examples~\cite{DBLP:conf/popl/FrankleOWZ16}, graded linear
types~\cite{DBLP:conf/lopstr/HughesO20}, ...).  Regardless of the kind
of specification, program synthesizers have to deal with two main
inherent sources of complexity: searching over a vast space of
(potentially) valid programs, and interpreting user intent.
%
In this work we will explore type-based synthesis where specifications
take the form of linear types, which are types that limit resource
usage in programs.  Concretely, we will explore the proof-theoretic
foundations of linear types via the Curry-Howard correspondence with
linear logic, viewing program synthesis under the lens of (linear
logic) bottom-up proof search.

>>>>

Specifications can take many forms (e.g.  polymorphic refinement
types~\cite{DBLP:conf/pldi/PolikarpovaKS16},
examples~\cite{DBLP:conf/popl/FrankleOWZ16}, graded linear
types~\cite{DBLP:conf/lopstr/HughesO20}).  Regardless of the kind
of specification, program synthesizers have to deal with two main
inherent sources of complexity: searching over a vast space of
(potentially) valid programs, and interpreting user intent.
%
In this work we will explore type-based synthesis where specifications
take the form of linear types, which are types that limit resource
usage in programs.  Concretely, we will explore the proof-theoretic
foundations of linear types via the Curry-Howard correspondence with
linear logic, viewing program synthesis under the lens of (linear
logic) bottom-up proof search.
